Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
tilde tests

\langName has a very simple type system, including only integers and lambda
abstractions, which include fixpoints by default, along with appropriate
security labels for both, as shown in Figure~\ref{fig:types}.  In \langName,
security labels specify confidentiality policies, specifying what other data the
labelled data can affect.\footnote{It is not difficult to imagine how to extend
our system to include integrity labels.  However, for the sake of simplicity, we
decided to concern ourselves with only confidentiality at first}  Data can only
be affected by items at the same label or lower (so high data can not affect low
labelled data).

@@

A reader familiar with the type system for \origLang will notice that our type
system does not include labels above the arrow in the function type, which would
normally give security bounds on side effects of the function, nor does it
include effect labels for exceptions.  These are dropped as a result of the
simplifications we made in defining \langName, since there are no side effects
or exceptions in the language.

@@

For the sake of being able to discuss how strong labels are in relation to a
type, we follow the example of Simonet and Pottier~\cite{InfoFlowML} and define
a ``guards'' relation between labels and types, denoted $l \guards t$, which
states that the label $l$ is at least as restrictive as the label on the type
$t$.  In other words, this requires that the type has at least $l$ for its
security label.  The two rules regarding this relationships for both types in
our language are given in Figure~\ref{fig:guard_rules}.

@@

Figure~\ref{fig:value_types} includes typing judgements for values in the
language, which are mostly straightforward with the exception of
\textsc{V-Bracket}, which we discuss below along with the type rules for
expressions.

>>>>

\langName has a very simple type system. It consists of only integers and lambda
abstractions (which include fixpoints by default) along with appropriate
security labels for both, as shown in Figure~\ref{fig:types}.  In \langName,
security labels denote confidentiality policies, which specify what other data the
labelled data can affect.\footnote{It is not difficult to imagine how to extend
our system to include integrity labels.  However, for the sake of simplicity, we
decided to concern ourselves with only confidentiality at first}  Data can only
be affected by items at the same label or lower (so high data can not affect low
data).

@@

A reader familiar with the type system for \origLang will notice that our type
system does not include labels above the arrow in the function type (which would
normally give security bounds on side effects of the function) nor does it
include effect labels for exceptions.  These are dropped as a result of the
simplifications we made in defining \langName, since there are no side effects
or exceptions in the language.

@@

For the sake of being able to discuss how strong labels are in relation to a
type, we follow the example of Simonet and Pottier~\cite{InfoFlowML} and define
a ``guards'' relation between labels and types, denoted $l \guards t$, which
states that the label $l$ is at least as restrictive as the label on the type
$t$.  In other words, this requires that the type has at least $l$ for its
security label.  The two rules regarding this relationship for both types in
our language are given in Figure~\ref{fig:guard_rules}.

@@

Figure~\ref{fig:value_types} includes typing judgements for values in the
language, which are mostly straightforward. The exception is
\textsc{V-Bracket}, which we discuss below.
